Artus -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-09-09 Core/doc/latex/paper.tex
paper: added abstract

\begin{abstract}
abstract
\end{abstract}

>>>>

\begin{abstract}
We present Artus, a data-processing application for high energy physics experiments. Artus is designed for large-scale data analysis in a collaborative environment.
The architecture design choices take into account typical challenges and are based on experiences with similar applications.
The structure of the framework and its advantages are described.
An example usecase and performance measurements are presented.
The framwork is well-tested and successfully used by several analysis groups.

\end{abstract}
